A performance comparison of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-29 latex/paper.tex

\TG{Talk about engine overhead: (1) where is it coming from? (2) 
explain the impact on data transfers with a graph.}

\TG{In the dicussion, get back to it and mention that (1) we don't
always observe that, (2) for data-intensive applications, overheads don't really matter
as reducing them increases data trasnfers.}

>>>>

Previous work showed that Dask has a the largest start-up overhead~\cite{Mehta:17}
when processing few subjects. Our Gantt charts show that Spark has a higher start-up
overhead. We think this is due to the larger amount of subjects we process.

The same study showed that Dask has a lower end-to-end runtime than Spark in a
neuroimaging analysis application. In our results, there is no significant difference
between the engines. We think this is because the applications we chose are highly
data-intensive while the one used in their study is compute intensive.

% \TG{Talk about engine overhead: (1) where is it coming from? (2) 
% explain the impact on data transfers with a graph.}

% \TG{In the dicussion, get back to it and mention that (1) we don't
% always observe that, (2) for data-intensive applications, overheads don't really matter
% as reducing them increases data trasnfers.}
